Tool-driven Revolutions in Archaeological Science

### 2019-08-09 analysis/paper/jcaa-paper.Rmd
updating the data analysis

---
title: "Tool-driven Revolutions in Archaeological Science"
author:
  - author 1
  - author 2
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
abstract: "There is an argument in philosophy of science that revolutions in science are either idea-driven or tool-driven. We explore this debate in light of recent efforts by many scientific disciplines to embrace methods to improve the reproducibility of their research. One of the most profound changes driven by this concern for reproducibility and transparency is from analysing data using tools dependent on point-and-clicking with a mouse in closed source software, to a new set of tools based on writing scripts in open source programming languages and making them openly available. We present bibliometric evidence for this change in ecology and in archaeology to test if the adoption of these new tools may be considered a revolution or some other process. We identify a citation effect for papers that use the open source programming language R. We discuss how computational approaches to improving reproducibility and transparency in archaeology are mediated and transformed by the use of R code."
---

@@

# We did a 'Cited Reference Search' in WoS for title "R: A Language and Environment for Statistical Computing" and author = "R Core Team", which is the output from  `citation()`. This function first appeared in 2004 https://github.com/wch/r-source/commits/9a5c086855d2e8fb07f670e3315871b2de31a4fd/src/library/base/inst/CITATION
#
# Note that before 2012 the authors were "R Development Core Team", and then it was simplified to "R Core Team" https://github.com/wch/r-source/commit/9a5c086855d2e8fb07f670e3315871b2de31a4fd#diff-80bb8a8b133a6204e9642d76791927e2
#
# This is our exact search string for WoS:

>>>>

---
title: "Tool-driven Revolutions in Archaeological Science"
author:
  - Sophie C. Schmidt
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
abstract: "There is an argument in philosophy of science that revolutions in science are either idea-driven or tool-driven. We explore this debate in light of recent efforts by many scientific disciplines to embrace methods to improve the reproducibility of their research. One of the most profound changes driven by this concern for reproducibility and transparency is from analysing data using tools dependent on point-and-clicking with a mouse in closed source software, to a new set of tools based on writing scripts in open source programming languages and making them openly available. We present bibliometric evidence for this change in ecology and in archaeology to test if the adoption of these new tools may be considered a revolution or some other process. We identify a citation effect for papers that use the open source programming language R. We discuss how computational approaches to improving reproducibility and transparency in archaeology are mediated and transformed by the use of R code."
---

@@

# We did a 'Cited Reference Search' in WoS for title "R: A Language and Environment for Statistical Computing" and author = "R Core Team", which is the output from  `citation()`. This function first appeared in 2004 https://github.com/wch/r-source/commits/9a5c086855d2e8fb07f670e3315871b2de31a4fd/src/library/base/inst/CITATION
#
# Note that before 2012 the authors were "R Development Core Team", and then it was simplified to "R Core Team" https://github.com/wch/r-source/commit/9a5c086855d2e8fb07f670e3315871b2de31a4fd#diff-80bb8a8b133a6204e9642d76791927e2
#
# We select all to get 185,121 results, then refine

#
# This is our exact search string for WoS:
